Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case

### 2019-01-23 ICML-submission/mistake-lower-bound-for-ignorant-algorithms.tex
Small fixes

\begin{proof}
By Lemma 6 of~\citet{Long-1995}, there exists a set of $N$ dimensional vectors
$z_1, z_2, \dots, z_N \in \R^{d-1}$ such that $\norm{z_1} = \norm{z_2} = \dots =
\norm{z_N} = 1$ and the angle between the vectors is $\measuredangle(z_i, z_j) \ge
\sqrt{40 \gamma}$. Since $\cos\theta \le 1-\theta^2/5$ for any $\theta \in
[-\pi,\pi]$, this implies that
\begin{align*}
\ip{z_i}{z_j} &= 1 && \text{if $i = j$,} \\
\ip{z_i}{z_j} &\le 1 - 8\gamma && \text{if $i \neq j$.}
\end{align*}

Define $v_i = (\frac12 z_i, \frac12)$, and $u_i = (\frac{1}{2} z_i, -\frac{1}{2}(1-4\gamma))$ for all $i \in \{1,2,\dots,N\}$.
It can be easily checked that for all $i$,
$\norm{v_i} \le 1$ and $\norm{u_i} \le 1$. Additionally,
$$
\ip{u_i}{v_j} = \frac{1}{4} \ip{z_i}{z_j} - \frac {1-4\gamma} 4 \; .
$$
Thus,
\begin{align*}
\ip{u_i}{v_j} &\ge \gamma && \text{if $i=j$,} \\
\ip{u_i}{v_j} &\le -\gamma && \text{if $i \neq j$.}
\end{align*}
\end{proof}

@@

Note that $B_{T_1}=1$, and for $t \geq T_1$ the adversary will switch to
``$\textsc{phase}=2$'' and has $y_t=2$. Therefore,
$\Exp[B_{t+1}=0|B_{t}=1]=\Pr[\widehat y_t=y_t~|~B_t=1] = \Pr[\widehat
y_t=2|B_t=1].$ Note that when $B_t=1$, by definition there exists a $\tau\le t$
with $p_\tau(1|x_\tau)\ge 1-q_0$, and the algorithm all makes mistakes at $\tau,
\tau+1, \ldots, t$. Since the algorithm is ignorant, and when
$\textsc{phase}=2$, the features all remain the same, we have
$p_t(1|x_t)=p_{t-1}(1|x_{t-1})=\cdots=p_\tau(1|x_\tau)\ge 1-q_0$. Thus we can
further upper bound $\Exp[B_{t+1}=0|B_{t}=1]$ by $\Pr[\widehat y_t=2|B_t=1]\leq
q_0$. Thus the second term in \eqref{equation:mistake_lower_bound_temp} can be
calculated as

>>>>

\begin{proof}
By Lemma 6 of~\citet{Long-1995}, there exists vectors $z_1, z_2, \dots, z_N \in
\R^{d-1}$ such that $\norm{z_1} = \norm{z_2} = \dots = \norm{z_N} = 1$ and the
angle between the vectors is $\measuredangle(z_i, z_j) \ge \sqrt{40 \gamma}$ for
$i \neq j$, $i,j \in \{1,2,\dots,N\}$. Since $\cos\theta \le 1-\theta^2/5$ for
any $\theta \in [-\pi,\pi]$, this implies that
\begin{align*}
\ip{z_i}{z_j} &= 1 && \text{if $i = j$,} \\
\ip{z_i}{z_j} &\le 1 - 8\gamma && \text{if $i \neq j$.}
\end{align*}

Define $v_i = (\frac{1}{2} z_i, \frac{1}{2})$, and $u_i = (\frac{1}{2} z_i,
-\frac{1}{2}(1-4\gamma))$ for all $i \in \{1,2,\dots,N\}$. It can be easily
checked that for all $i$, $\norm{v_i} \le 1$ and $\norm{u_i} \le 1$.
Additionally,
$$
\ip{u_i}{v_j} = \frac{1}{4} \ip{z_i}{z_j} - \frac {1-4\gamma} 4 \; .
$$
Thus,
\begin{align*}
\ip{u_i}{v_j} &\ge \gamma && \text{if $i=j$,} \\
\ip{u_i}{v_j} &\le -\gamma && \text{if $i \neq j$.}
\end{align*}
\end{proof}

@@

Note that $B_{T_1}=1$, and for $t \ge T_1$ the adversary will switch to
``$\textsc{phase}=2$'' and has $y_t=2$. Therefore,
$\Exp[B_{t+1}=0|B_{t}=1]=\Pr[\widehat y_t=y_t~|~B_t=1] = \Pr[\widehat
y_t=2|B_t=1].$ Note that when $B_t=1$, by definition there exists a $\tau\le t$
with $p_\tau(1|x_\tau)\ge 1-q_0$, and the algorithm all makes mistakes at $\tau,
\tau+1, \ldots, t$. Since the algorithm is ignorant, and when
$\textsc{phase}=2$, the features all remain the same, we have
$p_t(1|x_t)=p_{t-1}(1|x_{t-1})=\cdots=p_\tau(1|x_\tau)\ge 1-q_0$. Thus we can
further upper bound $\Exp[B_{t+1}=0|B_{t}=1]$ by $\Pr[\widehat y_t=2|B_t=1]\leq
q_0$. Thus the second term in \eqref{equation:mistake_lower_bound_temp} can be
calculated as
